---
title: "Sustainability Practices among Students in Zurich"
date: today
author:
  - name: Simon Schweizer
    orcid: 0009-0001-2771-4164
    email: sischweizer@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
abstract: "This study explores the differences in sustainability practices related to waste management between international and local Swiss students in Zurich, focusing on waste reduction, recycling, and reuse, alongside their awareness of local waste management systems."
execute:
  warning: false
editor: visual
format: 
  html:
    toc: true
    toc_depth: 3
    code_folding: show
bibliography: bibliography.bib
csl: apa.csl
---

# Introduction

This study examines sustainability practices among international and local students in Zurich, focusing on waste reduction, recycling, and reuse. It investigates the relationship between students' knowledge of the waste management system and their recycling behavior. Additionally, the research explores whether German language proficiency influences access to information about waste management. The basis of this study is the formulated research question: How do sustainability practices, such as waste reduction, recycling, and reuse, differ between international students and local Swiss students in Zurich, and is there a difference in their information status about the local waste management system? Crafting this well-defined research question is crucial in academic studies, as it helps in aligning the study's objectives with the expected outcomes [@fandino2019formulatingb].

# Methods

## Participant Recruitment

Participants for the survey were recruited from among ETH Zurich students. The survey was distributed as a Google Forms link, as a straightforward and rapid communication. This distribution method was selected to maximize response rates by facilitating easy access to the survey on mobile devices. The recruitment approach was informal, depending on students sharing the survey link within their networks, which resulted in an unknown distribution of participants across various fields of study and academic levels.

## Data Collection

The data collection utilized a structured Google Forms survey, designed to be intuitive and quick to complete, accommodating the busy schedules of students. The survey remained open for responses over a two-week period in May 2024. It included a series of both closed and open-ended questions to gather quantitative data and qualitative insights into students’ sustainability practices and perceptions.

### Survey Questions

-   **Demographics**: Questions about age, primary language, current residency in Zurich, and level of study to contextualize the data.
-   **Sustainability Practices**: Queries on the frequency of recycling and other waste management behaviors to assess active engagement.
-   **Knowledge and Perceptions**: Participants rated their knowledge of Zurich’s waste management system and evaluated its effectiveness.
-   **Challenges and Improvements**: This section includes questions to identify perceived challenges in waste management and suggestions for potential improvements in Zurich.

The Google Forms survey was designed to be completed within approximately one minute to ensure that it was not burdensome, thus encouraging comprehensive and thoughtful responses from the students.

## Statistical Analysis

Responses were exported from Google Forms and analyzed using descriptive statistics to summarize the demographics and identify overall patterns in sustainability practices and perceptions among the participants. Qualitative data from open-ended responses were thematically analyzed to extract common themes concerning challenges and proposed enhancements to the waste management system. The principles of data organization advocated by Broman and Woo (2018) guided the structuring and analysis of the survey data to enhance accuracy and facilitate effective analyses [@broman2018data]. Furthermore, adopting good practices in scientific computing, as suggested by Wilson et al. (2017), was crucial in ensuring the integrity and reproducibility of the data analysis process [@wilson2017gooda].

# Results

Let's dive into the results of the study, which are visually represented through a series of charts and tables. Each visualization and table is directly tied to the insights discussed below, providing a clear, data-driven foundation for the findings on student sustainability practices at ETH Zurich. The visualizations in this section were created using ggplot2, a powerful tool for data analysis and graphical representation, described extensively in Wickham's (2016) book on the subject [@zotero-80].

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(knitr)
library(tidyverse)
library(gt)

# Load the processed data
waste_data <- read_csv("../data/final/waste_survey.csv")
```

## Demographics and Knowledge

displays a stacked bar chart that illustrates the proportional responses by student group regarding their self-rated knowledge of Zurich's waste management system. This visualization is crucial for gauging the awareness levels across different student demographics, setting the stage for a deeper analysis into how this awareness translates into practical recycling behaviors.

```{r}
#| label: fig-engagement-levels
#| tbl-cap: "Proportional responses by student group and their self-rated knowledge of Zurich's waste management, shown in a stacked bar chart."

# Calculate proportions of knowledge ratings within each student group
proportion_data <- waste_data %>%
  group_by(student_group, knowledge_rating) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(student_group) %>%
  mutate(proportion = count / sum(count)) %>%
  ungroup()

# Convert knowledge_rating to a factor with levels in the desired order
proportion_data <- proportion_data %>%
  mutate(knowledge_rating = factor(knowledge_rating, levels = c(1, 2, 3, 4, 5)))

# Plot with reversed stacking order and ensure the proportions are correctly calculated
ggplot(proportion_data, aes(x = student_group, y = proportion, fill = factor(knowledge_rating))) +
  geom_bar(stat = "identity", position = position_stack(reverse = TRUE)) +
  geom_text(aes(label = scales::percent(proportion, accuracy = 0.1)),
            position = position_stack(vjust = 0.5, reverse = TRUE), size = 5, color = "white") +
  scale_fill_brewer(palette = "Set1") +
  labs(title = "Proportional Responses by Student Group and Knowledge Rating",
       x = "Student Group",
       y = "Proportion of Responses",
       fill = "Knowledge Rating") +
  theme_minimal(base_size = 15) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold"),
        axis.text = element_text(color = "black"))
```

## Recycling Frequency and Knowledge Correlation

@tbl-group-summary is an overview of the average ratings in recycling frequency and knowledge about the waste management system in zurich. Also the average rating of the perception if the recycling system is effective in zurich as an numerical rating from one as very bad to 5 as excelent.

```{r}
#| label: tbl-group-summary
#| tbl-cap: "Summary Statistics for Knowledge, Recycling Frequency, and System Effectiveness by Student Group"

# Calculating summary statistics including perceived effectiveness of the recycling system
summary_stats <- waste_data %>%
  group_by(student_group) %>%
  summarise(
    Mean_Knowledge = mean(knowledge_rating, na.rm = TRUE),
    Mean_Recycling_Frequency = mean(recycle_frequency_num, na.rm = TRUE),
    Mean_System_Effectiveness = mean(system_effectiveness, na.rm = TRUE)  # Adding mean for system_effectiveness
  )

# Displaying summary table using kable
kable(summary_stats, caption = "Summary Statistics for Knowledge, Recycling Frequency, and System Effectiveness by Student Group", format = "html", table.attr = "class='table table-striped'")
```

The relationship between students' self-reported knowledge of waste management and their actual recycling practices is depicted in the scatter plot in @fig-demographic-knowledge. This visual aid helps articulate the complex interaction between knowledge and behavior, revealing that higher awareness does not straightforwardly lead to more frequent recycling.

```{r}
#| label: fig-demographic-knowledge
#| tbl-cap: "Scatter plot showing the relationship between students' knowledge about waste management and their recycling frequency, differentiated by student group. Local Swiss students and international students are compared."

# Remove the outlier
waste_data <- waste_data %>%
  filter(!(knowledge_rating == 1 & recycle_frequency_num == 5))

# Create scatter plot with trend lines
ggplot(waste_data, aes(x = knowledge_rating, y = recycle_frequency_num, color = student_group)) +
  geom_point(size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed", size = 1, fullrange = TRUE) +
  labs(title = "Scatter Plot of Knowledge Rating vs. Recycling Frequency with Trend Lines",
       x = "Knowledge Rating",
       y = "Recycling Frequency",
       color = "Student Group") +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  scale_y_continuous(breaks = 1:5, labels = c("Never", "Rarely", "Sometimes", "Often", "Always"))
```

## Perceived Challenges and Suggestions

@tbl-summary-challanges summarizes the key challenges in waste management as identified by the students. This quantitative data complements the qualitative insights gathered, illustrating significant areas where Zurich’s waste management system could be enhanced.

```{r}
#| label: tbl-summary-challanges
#| tbl-cap: "Count of Answers for Biggest Challenges"

# Calculate count and percentage of answers for challenges
challenges_summary <- waste_data %>%
  count(biggest_challenge) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  slice_head(n = 5) %>%
  rename(answer = biggest_challenge)

# Create the table for challenges
challenges_summary %>%
  gt() %>%
  tab_header(title = "Biggest Challenges Summary") %>%
  cols_label(
    answer = "Biggest Challenge",
    percentage = "Percentage of Answers"
  ) %>%
  fmt_number(
    columns = vars(percentage),
    decimals = 2,
    suffixing = TRUE
  )
```

```{r}
#| label: tbl-summary-improvements
#| tbl-cap: "Count of Answers for Improvement Suggestions"
#| 

# Calculate count and percentage of answers for suggestions
suggestions_summary <- waste_data %>%
  count(improvement_suggestion) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  slice_head(n = 5) %>%
  rename(answer = improvement_suggestion)

# Create the table for suggestions
suggestions_summary %>%
  gt() %>%
  tab_header(title = "Improvement Suggestions Summary") %>%
  cols_label(
    answer = "Improvement Suggestion",
    percentage = "Percentage of Answers"
  ) %>%
  fmt_number(
    columns = vars(percentage),
    decimals = 2,
    suffixing = TRUE
  )
```

# Discussion

The survey data reveals a complex picture of sustainability practices among ETH Zurich students, highlighting several critical insights into their behaviors and perceptions regarding waste management:

## Knowledge and Awareness

The survey indicates a generally moderate to high level of awareness about Zurich's waste management system among ETH students, as most rated their knowledge as 3 or higher on a scale of 1 to 5 (@fig-engagement-levels). Theire is no clear difference in perceived knowledge between these student groups. On the one hand the only 5 score answers come from international students but on the other hand locals have a bigger range in 3 & 4 score answers.

This awareness, however, does not always translate into practice, as evidenced by the variability in recycling frequency depicted in the scatter plot @fig-demographic-knowledge . Such a discrepancy suggests that while students are aware, there may be other barriers to effective participation in recycling programs.

Still there is a clear visual trend as visualized by the trend line, that higher awareness or knowledge about waste management correlates with an higher recycling frequency. In other words, higher awareness leads to higher engagement in recycle practices.

## Effectiveness of the Waste Management System

A significant number of students believe that Zurich's waste management system is effective, which is reflected in the relatively high satisfaction scores (3 or above) (@tbl-group-summary). Despite this, many respondents identified specific challenges such as the need for more comprehensive waste sorting facilities and enhanced public education. This feedback points to opportunities for targeted improvements that could increase the system's efficiency and user friendliness (@tbl-summary-improvements).

## Challenges and Improvements

A recurring theme among the responses was the challenge of ensuring sufficient public participation in existing programs. Many students suggested that enhancing public education and outreach could address this issue (@tbl-summary-challanges). Additionally, the suggestion for more recycling stations and the introduction of incentive programs indicates a demand for infrastructure that supports more accessible and incentivized recycling practices.

# Conclusion

As demonstrated through the analyses in Figures 1 and 2, as well as Tables 1 and 2, there is a noticeable disconnect between the high awareness of waste management issues among ETH Zurich students and their varying recycling behaviors. These findings, derived from my individual research in the course, underscore the need for targeted educational programs and improved recycling infrastructure. Such efforts are vital in aligning knowledge with action, a key component of fostering sustainable practices in a global engineering context.

This study has highlighted several key findings regarding sustainability practices among ETH Zurich students:

-   **High Awareness but Variable Recycling Practices**: While students generally understand the functioning of Zurich's waste management system, their recycling habits vary widely. This variation suggests that knowledge alone is not enough to ensure consistent recycling practices as detailed in the visualization @fig-demographic-knowledge .

-   **Perceived Effectiveness and Areas for Improvement**: Students largely view the waste management system as effective, yet they also point out significant areas for improvement, particularly in terms of public education and infrastructure enhancement.

## Recommendations for Policy Makers

-   **Enhance Educational Programs**: Develop and implement targeted educational campaigns that not only inform but also motivate students to participate actively in sustainability practices.
-   **Increase Accessibility of Recycling Facilities**: Invest in more accessible recycling stations throughout the city, especially in areas frequented by students. Consider the implementation of solutions similar to those in other Swiss cities, like the plastic recycling-trash bags used in St. Gallen.
-   **Incentivize Recycling Practices**: Explore the introduction of incentive programs that reward sustainable behavior, potentially increasing participation rates among students.

## Further Research

Future studies should investigate the specific barriers that prevent students from recycling more frequently, despite high levels of awareness. Additionally, comparative studies involving other universities in Switzerland could provide broader insights into the effectiveness of various waste management strategies.

------------------------------------------------------------------------
